\section{Introduction}
Why is this an interesting question to ask and why would we care about the answer to this question or a solution to set a perfect goal? The Kickstarter policy is one or nothing. It means that if the amount of final pledged money is equal or higher than the goal, the fundraising campaign is successful. Otherwise, the fundraising campaign is fail and the creator receives nothing. If the creator overestimate the project goal, they will be fail, but if the creator set the project goal too low, they may not get attraction from community and gain less amount of money. Hence, predicting the amount of money or the number of backers are very important for Kickstarter creators to raise fund.

To our knowledge, There is only one research work try to predict how much fund a Kickstarter project can receive. Particularly, researchers at \cite{chung2015long} convert the problem of predicting the amount of final pledged money into classification problem by dividing such amount of final pledged money into different range. So the problem of predicting how much fund a Kickstarter project can receive will be the problem of predicting which range of money the project can receive.

Comparing to this work, our work is totally different, instead of predicting the range of final pledged fund, we build regression model to predict exactly the amount of money as well as the number of backers given a certain Kickstarter project.

Our contributions (or research questions) in this proposal are:
\begin{itemize}
\item Understand the influence of multiple factors toward the number of backers and the amount of final pledged money that a certain project can receive. We will show statistic values to illustrate for such influence.
\item Given a project, we propose a model to predict how much pledged fund the creator can receive
\item Finally, we Building a model to predict how many backers will fund for the project.
\end{itemize}